Principle of least action as a software development method

### 2022-12-15 ms.tex
fix

\documentclass[journal]{IEEEtran}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage[nopdftrailerid=true]{pdfprivacy}
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usepackage{hyperref}

\begin{document}
\DTLloaddb{keys-values}{python/bin/keys-values.csv}

@@

\section{Introduction}
Action is this.
Principle of least action is that.
So this is a sentence.

@@

although we could have a target regarding downloading external data this makes the Makefile non-portable for other projects thus this action needs to be done within the code
consistency across time from the developer perspective means that the technology used to program it will be available in the future
consistency across time from the user perspective practically means that the program should be finished from the point of view of features and only bug fixes might be developed
makes use of pre-existing standards: GNU standard for Makefile conventions and POSIX for the use of UNIX tools
the portability of the Makefile is achieved by using the mandatory UNIX utilities also mentioned by the GNU standard except for docker where needed
there is an inverse relationship between consistency and configurability
think about that subsets of standards have been used
time includes user interation to reach the target and total development time (including maintainance)
users care about the program, developers care about the code
we define a target of reducing the time required to create and navigate windows in a computing environment
we use Makefile to create the isolated environment (container) by bootstraping all required files if not already present and to make sure that subsequent changes to the requirements update the environment. The DAG should be as project agnostic as possible thus sentinel files are used
we use these specific targets for the Makefile (all, check, clean, help) because the first three are standard targets recommended by GNU standard targets and the fourth one is used in the linux kernel

@@

\section{Example use case: technical document}
This section provides a use case of the Makefile and also serves as a manual for developing using this method.
We train, validate and test MobilenetV2 neural networks~\cite{sandler2018mobilenetv2} in PyTorch, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep} and QMNIST~\cite{yadav2019cold}.
We use the default train, validation and test datasets and compare the use of ReLU, ReLU6\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in the MobilenetV2 model.

Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}: the number of epochs is $\DTLfetch{keys-values}{key}{epochs-num}{value}$, the batch size is $\DTLfetch{keys-values}{key}{batch-size}{value}$ and the learning rate for SGD is $\DTLfetch{keys-values}{key}{lr}{value}$.
Additionally, making use of random seed setting we consistenly get the same figures as shown in Fig.\ref{fig:loss} and Fig.\ref{fig:kernels}.
We also use the \textit{to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}):

\begin{figure}[!t]
	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/MNIST-loss.pdf}}
	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/FashionMNIST-loss.pdf}}
	\\
	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/KMNIST-loss.pdf}}
	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/QMNIST-loss.pdf}}
	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for all datasets.}\label{fig:loss}
\end{figure}

\begin{figure}[!t]
	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/MNIST-ReLU-kernels.pdf}}
	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/FashionMNIST-ReLU-kernels.pdf}}
	\\
	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/KMNIST-ReLU-kernels.pdf}}
	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/QMNIST-ReLU-kernels.pdf}}
	\caption{The first 25 kernels of the first convolutional layer of MobilenetV2 with ReLU for MNIST (upper-left), FashionMNIST (upper-right), KMNIST (lower-left) and QMNIST (lower-right).}\label{fig:kernels}
\end{figure}

\begin{table}[ht]
	\centering
	\caption{MobilenetV2 test dataset accuracies.}\label{table:table}
	\setlength\tabcolsep{4pt}
	\input{python/bin/metrics.tex}
\end{table}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage[nopdftrailerid=true]{pdfprivacy}

\begin{document}

@@

\section{Introduction}
Action is this.
Principle of least action is that.
So this is a sentence.
Software development practices like agile~\cite{abrahamsson2017agile}.

@@

although we could have a target regarding downloading external data this makes the Makefile non-portable for other projects thus this action needs to be done within the code
consistency across time from the developer perspective means that the technology used to program it will be available in the future
consistency across time from the user perspective practically means that the program should be finished from the point of view of features and only bug fixes might be developed
makes use of pre-existing standards: GNU standard for Makefile conventions and POSIX for the use of UNIX tools
the portability of the Makefile is achieved by using the mandatory UNIX utilities also mentioned by the GNU standard except for docker where needed
there is an inverse relationship between consistency and configurability
think about that subsets of standards have been used
time includes user interation to reach the target and total development time (including maintainance)
users care about the program, developers care about the code
we define a target of reducing the time required to create and navigate windows in a computing environment
we use Makefile to create the isolated environment (container) by bootstraping all required files if not already present and to make sure that subsequent changes to the requirements update the environment. The DAG should be as project agnostic as possible thus sentinel files are used
we use these specific targets for the Makefile (all, check, clean, help) because the first three are standard targets recommended by GNU standard targets and the fourth one is used in the linux kernel
The Makefile is only responsible for install the requirements inside the container.
The specific command arguments that e.g. check applications take should be done outside of the container to prevent the cache invalidation of the container.

@@

\section{Example use case: technical document}
This section provides a use case of the Makefile and also serves as a manual for developing using this method.
Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}.
Additionally, making use of random seed setting we consistenly get the same figures.
We also use the \textit{to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table.
